Sample size

### 2021-04-12 scripts/r/sample-size/sample-size.Rmd
:bug: - fix missing package in sample-size.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(brms)
library(extraDistr)
library(tidybayes)
```

@@

  meta_bm <- brm(
    es_mean | se(es_se) ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    cores = 4,
    backend = "cmdstanr", threads = threading(4),
    control = list(adapt_delta = 0.999)
  )

@@

@@

sims_40 <- tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  model = map(
    team_sd,
    ~run_simulations(.x, 40)
  )
)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(brms)
library(extraDistr)
library(HDInterval)
library(tidybayes)
```

@@

  meta_bm <- brm(
    es_mean | se(es_se) ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    cores = 4,
    backend = "cmdstanr", threads = threading(4),
    control = list(adapt_delta = 0.999),
  )

@@

saveRDS(sims, "./models/sim/sims.rds")

@@

saveRDS(sims_20, "./models/sim/sims_20.rds")

sims_40 <- tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  model = map(
    team_sd,
    ~run_simulations(.x, 40)
  )
)

saveRDS(sims_40, "./models/sim/sims_40.rds")
```
